NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-07-23 CW3CB3_4.Rmd
adding LCGA

---
title: "NDNS multilevel LCA CW2CB2 or CW2CB3"
author: "Chaochen Wang"
date: "19 July 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
---

@@

The number of classes in either level 1 were determined by

@@

2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes;

@@

4) In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

@@

library(kableExtra)
dt <- read.csv("../LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "---"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

From what is shown in the table that, although AIC, BIC, aBIC or entropy are improving with increasing n of classes, however, the Lo-Mendell-Rubun likelihood ratio test suggested that **n of classes higher than 4 did not fit the data necessarily better**. The null hypothesis of the LRT is that the fit of a n-class model is equal to that of the (n-1)-class model. So that p-value less than 0.05 indicates that the more complex model (the one with more latent classes) provides better fit to the data. We show the results from 3 classes (CW = 3) below.

@@

## Visualisation of level 1 latent classes (CW = 2)

@@

pp <- CW2CB2 %>% 
  group_by(CW) %>% 
  summarise(H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

@@

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Lunch at 1 pm low carb at night", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 Lunch at noon, high carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
  ylim(c(0,1))

@@

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual class 1\n(66.63%)",  "Individual class 2\n(33.37%)"))

@@

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2"), 
                        labels = c("Lunch at 1 pm low carb at night", "Lunch at noon, high carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual class 1\n(39.0%)",  "Individual class 2\n(28.05%)", 
                                   "Individual class 3\n(32.95%)"))

>>>>

---
title: "NDNS multilevel LCA CW2CB2 or CW2CB3"
author: "Chaochen Wang"
date: "19 July 2018"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    nature:
      highlightLines: true
editor_options: 
  chunk_output_type: console
---

@@

The number of classes in level 1 were determined by

@@

2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compares $q$ vs. $q-1$ class models, where $q$ is the number of latent classes;

@@

4) In the step of performing multilevel LCA, where LMR-LRT was not available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

@@

library(kableExtra)
dt <- read.csv("../LSHTMproject/Tablecsv/ndns_level1only.csv", header = T)
names(dt) <- c("N of classes", "N of free parameters","log-likelihood",  "AIC", "BIC", "aBIC", "Entropy", "Lo-Mendel-Rubin LRT")
dt[1,8] <- "--"
dt[2,8] <- "< 0.0001"
dt[3,8] <- "< 0.0001"
kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Level 1 class selection. (All data, n = 6155, 24483 data points)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(c(2,3), bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; AIC, Akaike information criterion; BIC, Bayesian information criterion; aBIC, adjusted BIC; Entropy, a pseudo-r-squared index; Lo-Mendel-Rubin LRT, likelihood ratio test comparing q classes models with q-1 classes models.")
```

From what is shown in the table that, although AIC, BIC, aBIC or entropy are improving with increasing n of classes, however, the Lo-Mendell-Rubun likelihood ratio test suggested that **n of classes higher than 4 did not fit the data necessarily better**. The null hypothesis of the LRT is that the fit of a n-class model is equal to that of the (n-1)-class model. So that p-value less than 0.05 indicates that the more complex model (the one with more latent classes) provides better fit to the data. We show the results from 2 classes (CW = 2) below.

@@

# (CW = 2) Level 1 latent classes

## Visualisation of level 1 latent classes

@@

pp <- CW2CB2 %>% 
  group_by(CW) %>% 
  summarise(H0_0 = sum(H0 == 0)/length(H0), 
            H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_0 = sum(H1 == 0)/length(H1),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_0 = sum(H2 == 0)/length(H2),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_0 = sum(H3 == 0)/length(H3),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_0 = sum(H4 == 0)/length(H4),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_0 = sum(H5 == 0)/length(H5),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_0 = sum(H6 == 0)/length(H6),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_0 = sum(H7 == 0)/length(H7),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_0 = sum(H8 == 0)/length(H8),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_0 = sum(H9 == 0)/length(H9),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_0 = sum(H10 == 0)/length(H10),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_0 = sum(H11 == 0)/length(H11),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_0 = sum(H12 == 0)/length(H12),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_0 = sum(H13 == 0)/length(H13),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_0 = sum(H14 == 0)/length(H14),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_0 = sum(H15 == 0)/length(H15),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_0 = sum(H16 == 0)/length(H16),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_0 = sum(H17 == 0)/length(H17),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_0 = sum(H18 == 0)/length(H18),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_0 = sum(H19 == 0)/length(H19),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_0 = sum(H20 == 0)/length(H20),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_0 = sum(H21 == 0)/length(H21),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_0 = sum(H22 == 0)/length(H22),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_0 = sum(H23 == 0)/length(H23),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

@@

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Lunch at 1 pm high carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 Lunch at noon, eat until late", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

@@

chart.data$CW <- factor(chart.data$CW, levels = c("2", "1"), 
                        labels = c("Lunch at 1 pm high carb breakfast", "Lunch at noon, eat until late"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual class 1\n(66.63%)",  "Individual class 2\n(33.37%)"))

@@

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2"), 
                        labels = c("Lunch at 1 pm high carb breakfast", "Lunch at noon, eat until late"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual class 1\n(39.0%)",  "Individual class 2\n(28.05%)", 
                                   "Individual class 3\n(32.95%)"))

# (CW = 3) Level 1 latent classes

## Visualisation of level 1 latent classes

CW3CB2 <- read_table2("results/50NDNS_CW3CB2.txt",
                         col_names = FALSE)

names(CW3CB2) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW3CB2 %>% 
  group_by(CW) %>% 
  summarise(H0_0 = sum(H0 == 0)/length(H0), 
            H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_0 = sum(H1 == 0)/length(H1),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_0 = sum(H2 == 0)/length(H2),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_0 = sum(H3 == 0)/length(H3),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_0 = sum(H4 == 0)/length(H4),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_0 = sum(H5 == 0)/length(H5),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_0 = sum(H6 == 0)/length(H6),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_0 = sum(H7 == 0)/length(H7),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_0 = sum(H8 == 0)/length(H8),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_0 = sum(H9 == 0)/length(H9),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_0 = sum(H10 == 0)/length(H10),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_0 = sum(H11 == 0)/length(H11),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_0 = sum(H12 == 0)/length(H12),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_0 = sum(H13 == 0)/length(H13),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_0 = sum(H14 == 0)/length(H14),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_0 = sum(H15 == 0)/length(H15),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_0 = sum(H16 == 0)/length(H16),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_0 = sum(H17 == 0)/length(H17),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_0 = sum(H18 == 0)/length(H18),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_0 = sum(H19 == 0)/length(H19),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_0 = sum(H20 == 0)/length(H20),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_0 = sum(H21 == 0)/length(H21),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_0 = sum(H22 == 0)/length(H22),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_0 = sum(H23 == 0)/length(H23),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Lunch at noon, high carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 Low carb at 6pm", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

# 
# 
ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
  geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
  ) +
  labs(title = "Class 3 Lunch at 1 pm, low carb at night", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

# 
# 
# ggplot(pp_long[pp_long$Class == 4, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
#   geom_point(size = 3) + 
#   geom_line(size = 1.5) + 
#   theme(axis.title = element_text(size = 18), 
#         axis.text = element_text(size = 18), 
#         axis.line = element_line(colour = "black"), 
#         panel.border = element_blank(), 
#         panel.background = element_blank(), 
#         legend.text = element_text(size = 15), 
#         legend.title = element_text(size = 15) 
#         # legend.position = "bottom", 
#         # legend.direction = "horizontal"
#   ) + 
#   labs(title = "Class 4 Low carb all day", x = "Hour of the day", y = "Probability",
#        color = "Carbohydrate\nintake") + 
#   scale_color_discrete(labels = c("< 50%", ">= 50%")) + 
#   ylim(c(0,1))
```

CW3CB2 <- CW3CB2 %>% 
  left_join(dt, by = "ID_DAY")

chart.data <- CW3CB2 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Lunch at 1 pm,\nlow carb at night", "Low carb at 6pm", "Lunch at noon,\nhigh carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2"), 
                        labels = c("Individual class 1\n(60.06%)",  "Individual class 2\n(39.94%)"))

```{r message=FALSE, warning=FALSE, echo=FALSE, paged.print=FALSE}

CW3CB3 <- read_table2("results/50NDNS_CW3CB3.txt",
                         col_names = FALSE)

names(CW3CB3) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CPROB9",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

CW3CB3 <- CW3CB3 %>% 
  left_join(dt, by = "ID_DAY")

chart.data <- CW3CB3 %>% 
  group_by(CB, CW) %>% 
  tally %>% 
  group_by(CB) %>% 
  mutate(pct = n/sum(n))

chart.data$CW <- factor(chart.data$CW, levels = c("3", "2", "1"), 
                        labels = c("Lunch at 1 pm,\nlow carb at night", "Low carb at 6pm", "Lunch at noon,\nhigh carb breakfast"))
chart.data$CB <- factor(chart.data$CB, levels = c("1", "2", "3"), 
                        labels = c("Individual class 1\n(41.76%)",  "Individual class 2\n(27.25%)", "Individual class 3\n(30.10%)"))

# (CW = 4) Level 1 latent classes

## Visualisation of level 1 latent classes

CW4CB2 <- read_table2("results/50NDNS_CW4CB2.txt",
                         col_names = FALSE)

names(CW4CB2) <- c("H0",
                      "H1",
                      "H2",
                      "H3",
                      "H4",
                      "H5",
                      "H6",
                      "H7",
                      "H8",
                      "H9",
                      "H10",
                      "H11",
                      "H12",
                      "H13",
                      "H14",
                      "H15",
                      "H16",
                      "H17",
                      "H18",
                      "H19",
                      "H20",
                      "H21",
                      "H22",
                      "H23",
                      "ID_DAY",
                      "AGE",
                      "SEX",
                      "CPROB1",
                      "CPROB2",
                      "CPROB3",
                      "CPROB4",
                      "CPROB5",
                      "CPROB6",
                      "CPROB7",
                      "CPROB8",
                      "CB",
                      "CW",
                      "MLCJOINT",
                      "ID")

pp <- CW4CB2 %>% 
  group_by(CW) %>% 
  summarise(H0_0 = sum(H0 == 0)/length(H0), 
            H0_1 = sum(H0 == 1)/length(H0), 
            H0_2 = sum(H0 == 2)/length(H0),
            H1_0 = sum(H1 == 0)/length(H1),
            H1_1 = sum(H1 == 1)/length(H1), 
            H1_2 = sum(H1 == 2)/length(H1),
            H2_0 = sum(H2 == 0)/length(H2),
            H2_1 = sum(H2 == 1)/length(H2), 
            H2_2 = sum(H2 == 2)/length(H2),
            H3_0 = sum(H3 == 0)/length(H3),
            H3_1 = sum(H3 == 1)/length(H3), 
            H3_2 = sum(H3 == 2)/length(H3),
            H4_0 = sum(H4 == 0)/length(H4),
            H4_1 = sum(H4 == 1)/length(H4), 
            H4_2 = sum(H4 == 2)/length(H4),
            H5_0 = sum(H5 == 0)/length(H5),
            H5_1 = sum(H5 == 1)/length(H5), 
            H5_2 = sum(H5 == 2)/length(H5),
            H6_0 = sum(H6 == 0)/length(H6),
            H6_1 = sum(H6 == 1)/length(H6), 
            H6_2 = sum(H6 == 2)/length(H6),
            H7_0 = sum(H7 == 0)/length(H7),
            H7_1 = sum(H7 == 1)/length(H7), 
            H7_2 = sum(H7 == 2)/length(H7),
            H8_0 = sum(H8 == 0)/length(H8),
            H8_1 = sum(H8 == 1)/length(H8), 
            H8_2 = sum(H8 == 2)/length(H8),
            H9_0 = sum(H9 == 0)/length(H9),
            H9_1 = sum(H9 == 1)/length(H9), 
            H9_2 = sum(H9 == 2)/length(H9),
            H10_0 = sum(H10 == 0)/length(H10),
            H10_1 = sum(H10 == 1)/length(H10), 
            H10_2 = sum(H10 == 2)/length(H10),
            H11_0 = sum(H11 == 0)/length(H11),
            H11_1 = sum(H11 == 1)/length(H11), 
            H11_2 = sum(H11 == 2)/length(H11),
            H12_0 = sum(H12 == 0)/length(H12),
            H12_1 = sum(H12 == 1)/length(H12), 
            H12_2 = sum(H12 == 2)/length(H12),
            H13_0 = sum(H13 == 0)/length(H13),
            H13_1 = sum(H13 == 1)/length(H13), 
            H13_2 = sum(H13 == 2)/length(H13),
            H14_0 = sum(H14 == 0)/length(H14),
            H14_1 = sum(H14 == 1)/length(H14), 
            H14_2 = sum(H14 == 2)/length(H14),
            H15_0 = sum(H15 == 0)/length(H15),
            H15_1 = sum(H15 == 1)/length(H15), 
            H15_2 = sum(H15 == 2)/length(H15),
            H16_0 = sum(H16 == 0)/length(H16),
            H16_1 = sum(H16 == 1)/length(H16), 
            H16_2 = sum(H16 == 2)/length(H16),
            H17_0 = sum(H17 == 0)/length(H17),
            H17_1 = sum(H17 == 1)/length(H17), 
            H17_2 = sum(H17 == 2)/length(H17),
            H18_0 = sum(H18 == 0)/length(H18),
            H18_1 = sum(H18 == 1)/length(H18), 
            H18_2 = sum(H18 == 2)/length(H18),
            H19_0 = sum(H19 == 0)/length(H19),
            H19_1 = sum(H19 == 1)/length(H19), 
            H19_2 = sum(H19 == 2)/length(H19),
            H20_0 = sum(H20 == 0)/length(H20),
            H20_1 = sum(H20 == 1)/length(H20), 
            H20_2 = sum(H20 == 2)/length(H20),
            H21_0 = sum(H21 == 0)/length(H21),
            H21_1 = sum(H21 == 1)/length(H21), 
            H21_2 = sum(H21 == 2)/length(H21),
            H22_0 = sum(H22 == 0)/length(H22),
            H22_1 = sum(H22 == 1)/length(H22), 
            H22_2 = sum(H22 == 2)/length(H22),
            H23_0 = sum(H23 == 0)/length(H23),
            H23_1 = sum(H23 == 1)/length(H23), 
            H23_2 = sum(H23 == 2)/length(H23))

ggplot(pp_long[pp_long$CW == 1, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 1 Lunch at noon, low carb 5pm,\nhigh carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

ggplot(pp_long[pp_long$CW == 2, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
  ) + 
  labs(title = "Class 2 Lunch at noon, low carb 6pm,\nhigh carb breakfast", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))

# 
# 
ggplot(pp_long[pp_long$CW == 3, ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
  geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
  ) +
  labs(title = "Class 3 Low carb late lunch (2pm) and \nLow carb dinner (7pm)", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c("Not eating", "< 50%", ">= 50%")) + 
  ylim(c(0,1))
